Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-01 paper/main.tex
Starting alignment GPU section
Working on gpu implementation discussion

\usepackage{iccv}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{amsfonts}
\usepackage{mydefs}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

@@

In the proposed CPU implementation, we instead solve a single alignment
instance at a time, using a multi-core BLAS library.  Recall that the L2 cache
can old up to 128 image vectors' worth of data.  Since we're only aligning data
for 1 gallery user at a time the working set of the problem fits into L2 cache,
resulting in significantly higher image alignment speed than previous cpu
implementations.

{\bf AY: A diagram should be used to illustrate how the jobs are distributed on a CPU architecture.}
%\subsection{Tuning the GEMV operation}
%When matrix-vector operations are called sequentially on the same data,
%the operation can be blocked so that each thread operates on the same block of data for each operation.
%For Single threaded MKL sgemv, Code took          0.0335823 msec per instance to run!
%For Automatic multi-threaded MKL sgemv, Code took 0.008179 msec per instance to run!
%For Manually multi-threaded MKL sgemv, Code took  0.0061276 msec per instance to run!

%\subsection{Tuning the Soft-Thresholding Operator}
%...Make sure there are no branches
%...Make sure there are no function calls
%...Make sure the loop gets automatically vectorized
%...Block the computation into work for different cpu cores
\subsection{GPU Implementation}
\label{sec:alignment_implementation_gpu}
{\bf AY: A diagram should be used to illustrate how the jobs are distributed on a CPU architecture.}

@@

\subsection{Simulation}

@@

\subsection{Face Alignment Benchmark}

\subsection{Face Recognition Benchmarks}

\subsection{Face Recognition Benchmark}

>>>>

\usepackage{iccv}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\usepackage{mydefs}

@@

During the course of development, many implementation strategies were tried.
Listed in order of increasing performance based on a synthetic benchmark of
the $\ell_1$ minimization step, they included:
\begin{enumerate}
\item A pure C++ implementation threaded and vectorized with OpenMP and icpc (200 ms).
\item An OpenCV (with MKL backend) implementation threaded with OpenMP similar to \cite{WagnerA2011-PAMI} (190ms.)
\item A straightforward MATLAB implementation (which uses threaded MKL internally) (60 ms.)
\end{enumerate}

In the proposed CPU implementation of the iterative alignment stage, we
therefore perform parallelization in a manner similar to the matlab code:
solving a single problem instance at a time, relying on the threaded version of
MKL BLAS for both multi-core and vector parallelism.  Why is this
implementation faster?  Recall that the L2 cache can old up to 128 image
vectors' worth of data.  Since we're only aligning data for 1 gallery user at a
time the working set of the problem fits into L2 cache, resulting in
significantly higher image alignment speed than previous cpu implementations.

%\subsection{Tuning the GEMV operation}
%When matrix-vector operations are called sequentially on the same data,
%the operation can be blocked so that each thread operates on the same block of data for each operation.
%For Single threaded MKL sgemv, Code took          0.0335823 msec per instance to run!
%For Automatic multi-threaded MKL sgemv, Code took 0.008179 msec per instance to run!
%For Manually multi-threaded MKL sgemv, Code took  0.0061276 msec per instance to run!

%\subsection{Tuning the Soft-Thresholding Operator}
%...Make sure there are no branches
%...Make sure there are no function calls
%...Make sure the loop gets automatically vectorized
%...Block the computation into work for different cpu cores

\subsection{GPU Implementation}
\label{sec:alignment_implementation_gpu}

This section discusses how to implement algorithm
\eqref{alg:iterative_alignment} on the GPU.  Like for the CPU case, many GPU
implementation strategies were explored during the course of our development,
and are only mentioned briefly.  Listed in order of increasing performance
based on a synthetic benchmark of the $\ell_1$ minimization step, they
included:
\begin{enumerate}
\item Solving a single problem instance at a time using Cublas\footnote{Nvidia provided BLAS implementation} (302 ms)
\item Pure CUDA C implementation solving one problem per SMP using cuda streams\footnote{Streams is a CUDA feature that allows multiple
kernels to be run concurrently} (70 ms)
\item Pure CUDA C implementation solving one problem per SMP using one large kernel call (36 ms)
\end{enumerate}

We attribute the low performance of Cublas in this benchmark to the relatively
low problem size. Cublas is intended to take advantage of the resources of the
entire gpu to solve a single large problem, and our problem size is too small
to hide the memory latency.  Effects of this will be seen again in the
benchmarks in section \ref{sec:simulation}.

Based on the strength of the results for our single-kernel implementation,

@@

\subsection{Simulation}
\label{sec:simulation}

@@

\subsection{Face Alignment Benchmark}
\label{sec:alignment_benchmark}

\subsection{Face Recognition Benchmarks}
\label{sec:recognition_benchmark}

\subsection{Face Recognition Benchmark}
\label{sec:pipeline_benchmark}
